running pipeline

### 2023-09-02 scripts/running_pipeline.Rmd
working on manuscript

data <- bind_cols(data, POW_names) %>% 
  relocate(starts_with('POW_'), .before = geometry)

dplyr::select(data, starts_with('POW')) |>
  sf::st_drop_geometry() |>
  utils::head()
```

@@

directions2site <- directions_grabber(data, api_key = SoS_gkey)

@@

?gs4_create
```

>>>>

data <- bind_cols(data, POW_names)

dplyr::select(data, starts_with('POW')) |>
  sf::st_drop_geometry() |>
  utils::head()

data <- powNAce(data)

@@

directions2site <- directions_grabber(data, api_key = SoS_gkey)
```

@@
